Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-04 ms.tex
abstract

\begin{abstract}
  We calculate steady-state, one-dimensional hydrodynamic profiles of
  hot gas in the nuclei of nominally quiescent galaxies for a range of
  central black hole mass $M_{\bullet}$, parameterized gas heating
  rate, and observationally-motivated stellar density profiles.  Mass
  is supplied to the circumnuclear medium by stellar winds, while gas
  is heated primarily by stellar winds, supernovae, and black hole
  feedback.  Analytic estimates are provided for the stagnation radius
  (where the radial velocity of the gas passes through zero) and the
  black hole mass accretion rate, $\dot{M}$, as a function of black
  hole mass and the gas heating efficiency, the latter of which is
  related to the star-formation history.  We assess the conditions
  under which radiative instabilities develop, separately in the case
  of a single burst of star formation and in the case of the average
  star formation history of galaxies hosting a given black hole
  mass. The measured nuclear X-ray luminosities, $L_{X}$, of a sample
  of quiescent black holes are combined with our results for $\dot{M}$
  to conclude that early-type quiescent black holes in the local
  universe are consistent with accreting in a locally thermally-stable
  state (on scales of the sphere of influence), possibly between
  cycles of thermal instability on larger galactic scales.  The
  maximum accretion rate of a thermally-stable flow is too low to
  explain the short growth times of low mass black holes in the local
  universe.  The latter must instead result from gas being fed in from
  large radii, either due to galaxy mergers associated with
  hierarchical growth or thermal instabilities on larger, galactic
  scales.  Our results have implications for attempts to constrain the
  occupation fraction of SMBHs in low mass galaxies using the mean
  $L_{\rm X}-M_{\bullet}$ correlation, as well as to the diversity of
  circumnuclear media densities encountered by relativistic jets from
  tidal disruption events.
\end{abstract}

>>>>

\begin{abstract}
  We calculate steady-state, one-dimensional hydrodynamic profiles of
  hot gas in the nominally quiescent galactic nuclei for a range of
  central black hole masses $M_{\bullet}$, parameterized gas heating
  rates, and observationally-motivated stellar density profiles.  Mass
  is supplied to the circumnuclear medium by stellar winds, while gas
  is heated primarily by stellar winds, supernovae, and black hole
  feedback.  Analytic estimates are derived for the stagnation radius
  (where the radial velocity of the gas passes through zero) and the
  black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and the gas heating efficiency, the latter of which is
  related to the star-formation history.  We assess the conditions
  under which radiative instabilities develop, separately in the case
  of a single burst of star formation and for the average
  star formation history, as predicted by cosmological simulations, of galaxies hosting black holes of a given mass. The measured nuclear X-ray luminosities, $L_{X}$, of nearby quiescent galactic nuclei and low luminosity AGN are combined with our results for $\dot{M}(M_{\bullet})$ to address whether the nuclei of most nearby galaxies are consistent with accreting in a steady-state, thermally-stable manner.  The maximum accretion rate of a thermally-stable flow is too low to explain the short average growth times of low mass black holes in the local
  universe.  The latter must instead result from gas being fed in from
  large radii, either due to galaxy mergers associated with
  hierarchical growth or thermal instabilities on larger, galactic
  scales.  Our results have implications for attempts to constrain the
  occupation fraction of SMBHs in low mass galaxies using the mean
  $L_{\rm X}-M_{\bullet}$ correlation, as well as applications to other topics, such as the predicted diversity of the
  circumnuclear media encountered by relativistic outflows from
  tidal disruption events.
\end{abstract}
